Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-08-15 submission_initial/paper_jasa blinded.tex
initially submitted materials

% Article top matter
\title{Validation of Visual Statistical Inference, Applied to Linear Models}
%\author{{Mahbubul Majumder, Heike Hofmann, Dianne Cook}
%\thanks{Mahbubul Majumder is Graduate Student (e-mail: mahbub72@gmail.com) , Heike Hofmann is Associate  Professor and Dianne Cook is Professor, Department of Statistics and Statistical Laboratory, Iowa State University, Ames, IA 50011-1210. This research is supported in part by the National Science Foundation Grant \# DMS 1007697.}}
\date{\vspace{-.7in}}
%\date{\today}  %\today is replaced with the current date
\maketitle

@@

There are some noticeable exceptions to this rule. In experiment 1, when $\beta=0, n=100, \sigma=5, rep=1$ people overwhelmingly chose a plot with much larger $p$-value, similarly, for 
parameters $\beta=5, n=300, \sigma=12, rep=3$, people tended to pick the plot with the second smallest $p$-value. 
For several of these exceptions, along with several easy lineups, a follow up experiment was conducted using an eye-tracker to examine which patterns or features participants are cueing on in making their choices \citep{zhao:2012}.
%(Lineups chosen for the eye-tracker experiment were in experiment 1, (1) $n=100, \beta=3, \sigma=5, rep=1$ (2) $n=100, \beta=5, \sigma=5, rep=1$ (3) $n=100, \beta=10, \sigma=12, rep=1$ and (4) $n=300, \beta=5, \sigma=5, rep=1$, and in experiment 2, (5) $n=100, \beta=3.5, \sigma=12, rep=1$ (6) $n=100, \beta=4.5, \sigma=12, rep=2$ (7) $n=300, \beta=1, \sigma=5, rep=1$ and (8) $n=300, \beta=1, \sigma=5, rep=2$.)

>>>>

% Article top matter
\title{Validation of Visual Statistical Inference, Applied to Linear Models}
%\author{
%{Mahbubul Majumder, Heike Hofmann, Dianne Cook}
%\thanks{Mahbubul Majumder is Graduate Student (e-mail: mahbub72@gmail.com) , Heike Hofmann is Associate  Professor and Dianne Cook is Professor, Department of
%Statistics and Statistical Laboratory, Iowa State University,
%Ames, IA 50011-1210. This research is supported in part by the
%National Science Foundation Grant \# DMS 1007697.}}
\date{\vspace{-.7in}}
%\date{\today}  %\today is replaced with the current date
\maketitle

@@

There are some noticeable exceptions to this rule. In experiment 1, when $\beta=0, n=100, \sigma=5, rep=1$ people overwhelmingly chose a plot with much larger $p$-value, similarly, for 
parameters $\beta=5, n=300, \sigma=12, rep=3$, people tended to pick the plot with the second smallest $p$-value. 
For several of these exceptions, along with several easy lineups, we followed up with a new experiment using an eye-tracker to examine which patterns or features participants are cueing on in making their choices \citep{zhao:2012:blinded}.
%(Lineups chosen for the eye-tracker experiment were in experiment 1, (1) $n=100, \beta=3, \sigma=5, rep=1$ (2) $n=100, \beta=5, \sigma=5, rep=1$ (3) $n=100, \beta=10, \sigma=12, rep=1$ and (4) $n=300, \beta=5, \sigma=5, rep=1$, and in experiment 2, (5) $n=100, \beta=3.5, \sigma=12, rep=1$ (6) $n=100, \beta=4.5, \sigma=12, rep=2$ (7) $n=300, \beta=1, \sigma=5, rep=1$ and (8) $n=300, \beta=1, \sigma=5, rep=2$.)
